---
title: "Figures"
author: "Samantha Peña"
date: "2025-01-15"
output: html_document
---
## Boysen waterhsed delineation figures##
## Export Watershed data 

###Step 1: Save/Export the Watershed from Model My Watershed:
After delineating the watershed on the website, look for an Export or Download option.
Export the watershed as a Shapefile, GeoJSON, or KML. Shapefiles are ideal for spatial analysis in R.
Download Files:
If exporting as a Shapefile, it will download as a .zip file containing multiple components (.shp, .shx, .dbf, .prj, etc.).
If exporting as a GeoJSON or KML, it will be a single file.
##Step 2:Step 2: Move the Data to Your R Working Directory
Place the downloaded file into your R working directory or specify its full file path.
If it is a .zip file, unzip it into a folder.
## Step 3: Load the Data into R
Now, you can load the watershed data into R using the sf package:

```{r setup, include=FALSE}
# Install and load necessary library
if (!require("sf")) install.packages("sf")
library(sf)

# Verify the file path
shapefile_path <- "~/Desktop/LAKE_DATA/Figures/Figures/Continental_US_from_NHDplus_v2-2"

# Load the shapefile into R as an sf object
watershed_sf <- st_read(shapefile_path)

watershed_sf <- st_read('~/Desktop/LAKE_DATA/Figures/Figures/Continental_US_from_NHDplus_v2-2')


# View the watershed data
print(watershed_sf)

# Plot the watershed
plot(st_geometry(watershed_sf))

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
